The Community Land Model, version 5.1 \\ One-at-a-time Parameter Perturbation Ensemble

### 2023-08-31 ms/ms.tex
Updates from Overleaf

Relative to CLM5.0, version 5.1 includes minor bug fixes, parameter adjustments \cite{birch2021}, and the implementation of biomass heat storage \cite{swenson2019}. The PPE experiment required additional code modifications to enable systematic variation of the full suite of model parameters (many of which were previously `hard-coded', i.e., written directly as numerical values in the model source code). We utilized the biogeochemical cycling version of CLM, which includes active carbon and nitrogen cycles. This is as opposed to the satellite phenology mode, which is driven by observed canopy properties and thus has fewer internal feedbacks, and was explored in \citeA{dagon2020}. We used the model in land-only mode driven by observed meteorological forcing from the GSWP3v1 reanalysis product (\url{http://hydro.iis.u-tokyo.ac.jp/GSWP3/}), with the crop model turned off.

>>>>

Relative to CLM5.0, version 5.1 includes minor bug fixes, parameter adjustments, and the implementation of biomass heat storage \cite{swenson2019}. The PPE experiment required additional code modifications to enable systematic variation of the full suite of model parameters (many of which were previously `hard-coded', i.e., written directly as numerical values in the model source code). We utilized the biogeochemical cycling version of CLM, which includes active carbon and nitrogen cycles. This is as opposed to the satellite phenology mode, which is driven by observed canopy properties and thus has fewer internal feedbacks, and was explored in \citeA{dagon2020}. We used the model in land-only mode driven by observed meteorological forcing from the GSWP3v1 reanalysis product (\url{http://hydro.iis.u-tokyo.ac.jp/GSWP3/}), with the crop model turned off.
